Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-29 CAV 2025 TODO/Paper_noProof.tex
exp
all

        To handle complex instances, we revisit a divide-and-conquer approach to break down the complexity: instead of few complex BaB calls, we rely on many small {\em partial} MILP calls. The crucial step is to select very few but very important ReLUs to treat using (costly) binary variables. The previous attempts were suboptimal in that respect. In this paper, we propose a novel {\em solution-aware} ReLU ranking (SAR), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU ranking (GR) functions. We compare them theoretically as well as experimentally. Surprisingly perhaps, the most accurate solution (SAR) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GR) to {\em rank} within this selection. Compared with previous attempts, SAR reduces the number of integer variables by around 4 times while maintaining the same level of accuracy. Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.

>>>>

        To handle complex instances, we revisit a divide-and-conquer approach to break down the complexity: instead of few complex BaB calls, we rely on many small {\em partial} MILP calls. The crucial step is to select very few but very important ReLUs to treat using (costly) binary variables. The previous attempts were suboptimal in that respect. In this paper, we propose a novel {\em solution-aware} ReLU scoring (SAS), as well as adapt the BaB-SR and BaB-FSB branching functions as {\em global} ReLU scoring (GS) functions. We compare them theoretically as well as experimentally. Surprisingly perhaps, the most accurate solution (SAS) for {\em selecting} ReLUs to treat as binary variables is different from the most efficient solution (GS) to {\em rank} within this selection. Compared with previous attempts, SAS reduces the number of integer variables by around 4 times while maintaining the same level of accuracy. Implemented in {\em Hybrid MILP}, calling first $\alpha,\beta$-Crown with a short time-out to solve easier instances, and then partial MILP, produces a very accurate yet efficient verifier, reducing by up to $40\%$ the number of undecided instances to low levels ($8-15\%$), while keeping a reasonable runtime ($46s-417s$ on average per instance), even for fairly large CIFAR CNNs with 20 000 nodes.

### 2025-01-29 CAV 2025 TODO/experiments.tex
exp
all

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the scoring function to select neurons to open, 
we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
We tested over the $\vx=37$th image in the CIFAR dataset.
To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB(a) - \LB(a)$. The average uncertainty of layer $\ell$ is 
$$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$$

\begin{figure}[b!]
	\centering
	\vspace*{-0.3cm}
	\includegraphics[height=7cm]{open.png}.
	\vspace*{-0.4cm}
	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
	\label{fig_table3}
\end{figure}

@@

\begin{table}[t]	
	\centering
	\begin{tabular}{|c||c c|c c|c c|c c|}
		\hline
		  & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
		 order & uncert & time & uncert & time & uncert & time & uncert & time \\
		\hline \hline
		Gurobi &  & 252s & &  & & &   & 306s  \\ 
		SAS (static) &  & 448s & &  & & &   & 971s \\
		GS (static) & & {\bf 251s} & &  &  & &  & {\bf 281s} \\ \hline
	\end{tabular}
	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
	\label{table.order}
	%\vspace{-0.6cm}
\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c|c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
		\hline
		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & $-$ & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown and Hybrid MILP on 7 DNNs (average runtime per image). The 6 first DNNs are hard instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.}
	\label{table_hybrid}
	\end{table}

@@

@@

\begin{figure}[t!]
	\begin{centering}
\includegraphics[scale=0.6]{epsilon.png}.
\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ on each of the 20 first images of MNIST.}
\label{fig2}
	\end{centering}
\end{figure}

{\em Analysis}: in 90\% of the cases, Hybrid MILP is very close to the upper bound. On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible that the falsifier missed a closer attack to robustness.

Compared with $\alpha,\beta$-CROWN, Hybrid MILP is much closer to the upper bound, except for 2 cases (images 8 and 18) where $\alpha,\beta$-CROWN is already very close to the upper bound. On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.

Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
We report result from \cite{cutting} pertinent to the DNNs we tested, and copy the comparison with $\alpha,\beta$-Crown. While results are similar to ours, they do not use exactly the same number of input images than in our test, and thus it is not directly comparable. 
On CNN-B-Adv, GCP-CROWN is $2\%$ more accurate (with higher runtime) than 
$\alpha,\beta$-Crown with 90s TO, so it is safe to consider that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO,  is significantly more accurate than GCP-CROWN on this quite large DNN.

Notice that results for other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported on these DNNs \cite{crown}, with unfavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on hard instances either, even on the smallest hard DNN. Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em hard} MNIST DNNs at several time-out settings. Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible. Details can be found in the appendix. Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.

>>>>

%The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes,  to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.
To measure the impact of the scoring function to select neurons to open, 
we considered the largest complex CNN-B-Adv, with 20 000 nodes. 
We tested over the $\vx=37$th image in the CIFAR dataset.
To measure the accuracy, we measure the uncertainty of all nodes in the 4th layer:
the uncertainty of a node is the range between its computed lower and upper bound. 
We then average the uncertainty among all the nodes of the layer.
Formally, the uncertainty of a node $a$ with bounds $[\LB,\UB]$ is uncert$(a) = \UB(a) - \LB(a)$. The average uncertainty of layer $\ell$ is 
$\dfrac{\sum_{a\in l} \text{uncert}(a)}{size(\ell)}.$

\begin{figure}[t!]
	\centering
	\vspace*{-0.3cm}
	\includegraphics[height=7cm]{open.png}.
	\vspace*{-0.4cm}
	\caption{Average uncertainty of pMILP for neurons of the fourth layer of CNN-B-Adv, 
	when opening between 0 and 30 ReLUs, chosen randomly vs Huang \cite{DivideAndSlide} vs 
	$s_{FSB}$ vs $\Utility$ (with time-out=900s).}
	\label{fig_table3}
\end{figure}

@@

\begin{table}[b!]	
	\centering
	\begin{tabular}{|c||c c|c c|c c|c c|}
		\hline
		  & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
		 order & uncert & time & uncert & time & uncert & time & uncert & time \\
		\hline \hline
		Gurobi &  & 252s & &  & & &   & 306s  \\ 
		SAS (static) &  & 448s & &  & & &   & 971s \\
		GS (static) & & {\bf 251s} & &  &  & &  & {\bf 281s} \\ \hline
	\end{tabular}
	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
	\label{table.order}

\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l||c|c|c||c||c||}
		\hline \hline
		 & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & $\alpha,\beta$-Crown & Refined & \bf Hybrid \\ 
		 Network & TO=10s & TO=30s & TO=2000s & $\beta$-Crown & \bf MILP \\ 
		\hline
		MNIST 5$\times$100 & 57\% (6.9s) & 55\% (18.9s) & 50\% (1026s) & 13\% 
		(92s) & 13\% \bf (46s) \\ \hline
		MNIST 5$\times$200 & 50\% (6.5s) & 47\% (17s) & 46\% (930s) & 9\% (80s) & \bf 8\% (71s) \\ \hline
		MNIST 8$\times$100 & 63\% (7.2s) & 58\% (20s) & 58\% (1163s) & 21\% (102s) & \bf 15\% (61s) \\ \hline
		MNIST 8$\times$200 & 56\% (6.8s) & 55\% (18s) & 54\% (1083s) & 16\% (83s) & \bf 8\% (78s) \\ \hline
		MNIST 6$\times$500 & 53\% (6.4s) & 51\% (16s) & 50\% (1002s) & $-$ & 
		\bf 10\% (402s) \\ \hline
		CIFAR CNN-B-adv & 28\% (4.3s) & 22\% (8.7s) & 20\% (373s) & $-$ & \bf 11\% (417s) \\ \hline \hline
		CIFAR ResNet & 0\% (2s) & 0\% (2s) & 0\% (2s) & $-$ & 0\% (2s) \\ \hline \hline
	\end{tabular}
	\caption{Undecided images ($\%$, {\em lower is better}) as computed by $\alpha,\beta$-Crown, Refined $\beta$-Crown and Hybrid MILP on 7 DNNs (average runtime per image). The 6 first DNNs are hard instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify), provided for reference.
	\vspace{-1cm}}
	\label{table_hybrid}
	\end{table}

@@

Interestingly, GCP-CROWN \cite{cutting} is slightly more accurate than $\alpha,\beta$-Crown on the DNNs we tested, but necessitates IBM CPLEX solver, which is not available to us.
We provide in Table \ref{table_gcp} results from the Table 3 page 9 of \cite{cutting}, experimenting with different verifiers on the most interesting CIFAR CNN-B-Adv. Notice that results are not exactly comparable with ours because the testing images are not the same (ours has $62\%$ upper bound while \cite{cutting} has $65\%$ upper bound, so the image set in \cite{cutting} are slightly easier). There, GCP-CROWN is $2\%$ more accurate (with higher runtime) than $\alpha,\beta$-Crown with 90s TO, so we can deduce that Hybrid MILP, which is $9\%$ more accurate than $\alpha,\beta$-Crown with 2000s TO, is significantly more accurate than GCP-CROWN.

\begin{table}[b!]
	\centering
	\begin{tabular}{||c||c|c|c|c|c||}
		\hline
		Upper Bound & SDP-FO & PRIMA & refined $\beta$-Crown & $\beta$-Crown & GCP-Crown \\  \hline
		65\% & 32.8\% & 38\% & 27\% & 46.5\% & 48.5\% \\
		$\epsilon = 2/255$ & $>25$h & $344$s & $361$s & $32$s &  $58$s  \\  \hline
	\end{tabular}
	\caption{Images verified by different verifiers on CIFAR CNN-B-adv from \cite{cutting}.
	Results are not directly comparable with Tables \ref{table_beta},\ref{table_hybrid}.}
	\label{table_gcp}
	\vspace{-0.3cm}
\end{table}

Results on other networks from other verifiers (PRIMA \cite{prima}, SDP-FO \cite{SDPFI}, etc) were already reported \cite{crown} on other tested DNNs, with unfavorable comparison vs $\alpha,\beta$-CROWN. Further, we reported accuracy of NNenum \cite{nnenum}, Marabou \cite{Marabou,Marabou2}, respectively 4th, 3rd of the last VNNcomp'24 \cite{VNNcomp24}, as well as full MILP \cite{MILP} in Table \ref{table_complete}, showing that these verifiers are not competitive on complex (even small) instances. Concerning MnBAB \cite{ferrari2022complete}, we tested it in appendix, and it compares slightly unfavorably in time and accuracy towards $\alpha,\beta$-CROWN on CNN-B-Adv and {\em complex} MNIST DNNs at several time-out settings. Last, Pyrat \cite{pyrat} (2sd in the latest VNNComp) is not open source, which made running it impossible. Details can be found in the appendix. Also, ablation studies showing what each feature of Hybrid MILP is bringing can be found in the appendix.

@@

\begin{figure}[t!]
	\begin{centering}
\includegraphics[scale=0.6]{epsilon.png}.
\caption{$\epsilon$-robustness proved after $10 000s$ for $6 \times 500$ for the 20 first images.}
\label{fig2}
	\end{centering}
\end{figure}

{\em Analysis}: in 90\% of the cases, Hybrid MILP is very close to the upper bound. On 2 images (10 and 13), Hybrid MILP is far from the upper bound: these are also the ones where the upper bound is the highest, so it is possible that the falsifier missed a closer attack to robustness. On average, the $\epsilon$-gap to upper bound is $0.014$ for Hybrid MILP, 3 times smaller than the $0.042$ gap for $\alpha,\beta$-CROWN.

### 2025-01-29 CAV 2025 TODO/formula.tex
all

Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
%(this can be obtained very efficiently by {\em one} call to an LP solver).
Function
$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
would however be very time consuming when the number of neurons $a$ to evaluate is large.
{\color{blue} 
The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig. \ref{fig_table3}).

@@

Notice that $\Utility$ does not need to consider bias explicitly, unlike $s_{FSB},s_{SR}$,
as they are already accounted for in the solution considered. 
There are two main differences with $s_{FSB}$: 
First, $\Delta(\hat{a})$ is defined exactly, with $\ReLU(\sol(a))-\sol(\hat{a})$,
whereas the corresponding $\Delta_{FSB}(\hat{a})$ is approximated as $\LB(a) r(a)$, 
which is only an upper bound of $\ReLU(\sol(a))-\sol(\hat{a})$.
More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the case when $W_{bz}<0$, correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
Assuming that the solution to maximize $z$ does not change when opening $\ReLU(a)$
on neurons independant of $a$, then $\Utility$ is exact. This is not the case for $s_{FSB}$ because of the two previously mentionned cases. Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):
}

>>>>

Consider $(sol(n))_{n \leq z} = (\Sol\_\max_\emptyset^z(n))_{n \leq z}$, a solution maximizing the value for $z$ when all ReLU use the LP relaxation.
%(this can be obtained very efficiently by {\em one} call to an LP solver).
Function
$\Improve\_\max^z(n)=$ $\sol(z) - \Sol\_\max_{\{n\}}^z(z)$, 
accurately represents how much opening neuron $n < z$ reduces the maximum computed for $z$
compared with using only LP. 
We have $\Improve\_\max^z(n)\geq 0$ as $\Sol\_\max_{\{n\}}^z$ fulfills all the constraints of 
$\mathcal{M}_\emptyset$, so $\Sol\_\max_{\{n\}}^z(z) \leq \sol(z)$.
Similarly, we define ($\Sol\_\min_\emptyset^z(n))_{n \leq z}$ and 
$\Improve\_\min^z(n)$. Calling MILP on $\mathcal{M}_{\{n\}}$ for every neuron $n \leq z$
would however be very time consuming when the number of neurons $a$ to evaluate is large.
The main novelty of our SAS function is that it uses a (single) LP call to compute $(sol(n))_{n \leq z}$, with negligible runtime wrt the forthcoming  $\MILP_X$ call, and yet accurately approximates $\Improve\_\max^z(n)$ to choose a meaningful set $X$ of open nodes (Fig. \ref{fig_table3}).

@@

Notice that $\Utility$ does not need to consider bias explicitly, unlike $s_{FSB},s_{SR}$,
as they are already accounted for in the solution considered. 
There are two main differences with $s_{FSB}$: 
First, $\Delta(\hat{a})$ is defined exactly, with $\ReLU(\sol(a))-\sol(\hat{a})$,
whereas the corresponding $\Delta_{FSB}(\hat{a})$ is approximated as $\LB(a) r(a)$, 
which is only an upper bound of $\ReLU(\sol(a))-\sol(\hat{a})$.
More importantly, the corresponding $\Delta_{FSB}(\hat{b})$ is always $r(b) \Delta(b)$, whereas SAS adapts to the case when $W_{bz}<0$, correctly considering the 0 phase of $ReLU(b)$ when $\sol(b)\geq 0$, and the ID phase when $\sol(b)<0$.
Assuming that the solution to maximize $z$ does not change when opening $\ReLU(a)$
on neurons independant of $a$, then $\Utility$ is exact. This is not the case for $s_{FSB}$ because of the two previously mentionned cases. Further, even when the global solution changes, we can show that $\Utility$ is a safe overapproximation, which does not hold for $s_{FSB},s_{SR}$ (because of the case $sol(b) > 0$):

### 2025-01-29 CAV 2025 TODO/introduction.tex
all

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 5$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 8$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 8$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are complex instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.}
	\label{table_beta}
	\vspace{-0.3cm}
\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
		  \\  \hline
		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
	\end{tabular}
\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).}
\label{table_complete}
\end{table}

Other standard non-BaB methods such as Marabou 2.0, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image. It appeared pointless to test these verifiers on larger networks.

@@

	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global ranking (GR) functions to choose ReLU for pMILP. 
	These revealed to be much more accurate than the simple heuristic in 
	\cite{DivideAndSlide}. We uncover however one case (out of 4) where the exact function that GR tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode. This implies that these strategies may not be that accurate, because they do not know the mode to choose from. We then designed a novel solution-aware ranking (SAR), which uses the solution of a unique LP call, that provides the mode to consider. Theoretically, we show that SAR is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAR value implies that the ReLU is unnecessary. Experimentally, we further show that SAR is very close to the actual improvement, closer than GR, and that overall, the accuracy from SAR is significantly better than GR.  Compared with the heuristic in \cite{DivideAndSlide}, SAR is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GR would be better suited, which we verify experimentally.

>>>>

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network & Accuracy & Upper  & $\alpha,\beta$-Crown& $\alpha,\beta$-Crown & $\alpha,\beta$-Crown \\ 
		Perturbation &   & Bound & TO=10s & TO=30s & TO=2000s\\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 33\% & 35\% & 40\%   \\
		$\epsilon = 0.026$ &  &  & 6.9s &  18.9s &  1026s  \\  \hline
		MNIST 5$\times$200 & 99\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
		$\epsilon = 0.015$ & &  & 6.5s &  16.6s &  930s  \\  \hline
		MNIST 8$\times$100 & 97\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
		$\epsilon = 0.026$ &  &  & 7.2s &  20.1s &  930s  \\  \hline
		MNIST 8$\times$200 & 97\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
		$\epsilon = 0.015$ & &  & 6.8s &  18.2s &  1083s  \\  \hline
		MNIST 6$\times$500 & 100\%  & 94\%  & 41\%  & 43\%  & 44\%   \\ 
		$\epsilon = 0.035$ & &  & 6.4s &  16.4s &  1003s  \\  \hline
		CIFAR CNN-B-adv & 78\%  & 62\%  &  34\% & 40\%  & 42\%   \\
		$\epsilon = 2/255$&  &  & 4.3s & 8.7s & 373s  \\ \hline \hline
		CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
		$\epsilon = 2/255$ &  &  & 2s & 2s & 2s  \\ \hline
	\end{tabular}
	\caption{Images verified by $\alpha,\beta$-Crown with different time-outs (TO) on 7 DNNs, and average runtime per image. The 6 first DNNs are complex instances. The last DNN (ResNet) is an easy instance (trained using Wong to be easy to verify, but with a very low accuracy level), provided for reference.
	\vspace{-0.5cm}}
	\label{table_beta}
\end{table}

@@

\begin{table}[t!]
	\centering
	\begin{tabular}{||l|c|c||c|c|c||}
		\hline
		Network &  Accuracy & Upper  & Marabou 2.0 & NNenum &  Full MILP  \\ \hline
		MNIST 5$\times$100 & 99\% & 90\% & 28\% & $49\%$ & 40 \%    \\
		$\epsilon = 0.026$ & &  &6200s &  4995s & 6100s
		  \\  \hline
		%  MNIST 5$\times$100 & 99\% & 90\% & 28\% & $46\%$ & 37 \%    \\
		%  TO=2000s & &  & 1250s  & 1194s & 1466s \\  \hline	
	\end{tabular}
\caption{Result of non-BaB methods on the hard $5 \times 100$ with TO = 10 000s. 
%Because the instances are hard, most test time-out at the global threshold of 10.000s per image, and 
Only NNenum verifies more instances (9\% out of 50\% undecided images) than $\alpha,\beta$-Crown (40\%), at the cost of a much larger runtime (4995s vs 1026s).
\vspace{-0.5cm}}
\label{table_complete}
\end{table}

Other standard non-BaB methods such as Marabou, NNenum or a Full MILP encoding, show similar poor performance on such complex instances as well, even with a large 10 000s Time-out: Table \ref{table_complete} reveals that only NNenum succeeds to verify images not verified by $\alpha,\beta$-Crown, limited to 9\% more images out of the 50\% undecided images on $5 \times 100$, and with a very large runtime of almost 5000s per image. It appeared pointless to test these verifiers on larger networks.

@@

	\item On the first question, we adapted from BaB-SR \cite{BaB} and FSB \cite{FSB}, which choose branching nodes for BaB, global scoring (GS) functions to choose ReLU for pMILP. 
	These revealed to be much more accurate than the simple heuristic in 
	\cite{DivideAndSlide}. We uncover however one case (out of 4) where the exact function that GS tries to approximate depends heavily upon the mode of the ReLU function, giving very different result for each mode. This implies that these strategies may not be that accurate, because they do not know the mode to choose from. We then designed a novel solution-aware scoring (SAS), which uses the solution of a unique LP call, that provides the mode to consider. Theoretically, we show that SAS is always an over-approximation of the real improvement (Proposition \ref{prop2}), which implies that a small SAS value implies that the ReLU is unnecessary. Experimentally, we further show that SAS is very close to the actual improvement, closer than GS, and that overall, the accuracy from SAS is significantly better than GS.  Compared with the heuristic in \cite{DivideAndSlide}, SAS is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})).We however explain why focusing on a solution may not be appropriate to choose branching order within this selection, and that GS would be better suited, which we verify experimentally.
